\pkg{NeuralNetTools}: Visualization and Analysis Tools for Neural Networks

### 2015-11-30 nnt_manu.Rnw
contact update

%% almost as usual
\author{Marcus W. Beck\\Oak Ridge Institute for Science and Education\\US Environmental Protection Agency}
\title{\pkg{NeuralNetTools}: Visualization and Analysis Tools for Neural Networks}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Marcus W. Beck\\
  Oak Ridge Institude for Science and Education\\
  US Environmental Protection Agency\\
  National Health and Environmental Effects Research Laboratory\\
  Gulf Ecology Division, 1 Sabine Island Drive\\
  Gulf Breeze, Florida, 32561, USA\\
  Telephone: +1/850/934-2480\\
  E-mail: \email{beck.marcus@epa.gov}
}

>>>>

%% almost as usual
\author{Marcus W. Beck\\US Environmental Protection Agency}
\title{\pkg{NeuralNetTools}: Visualization and Analysis Tools for Neural Networks}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Marcus W. Beck\\
  US Environmental Protection Agency\\
  National Health and Environmental Effects Research Laboratory\\
  Gulf Ecology Division, 1 Sabine Island Drive\\
  Gulf Breeze, Florida, 32561, USA\\
  Telephone: +1/850/934-2480\\
  E-mail: \email{beck.marcus@epa.gov}
}
